\documentclass[12pt]{article}

%Technometrics specified margins:

% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{1}

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.3in}%
\addtolength{\topmargin}{-.8in}%
\usepackage{psfrag,epsf,enumerate}

%\usepackage[margin=1.1in]{geometry}
\usepackage{color, amssymb, amsmath,bm,verbatim}
\usepackage{rotating, subfig, setspace, tikz}
\usepackage{graphicx, graphics, epsfig}
\usepackage{multirow,multicol}
\usepackage{natbib}
\newcommand{\tr}{{\mathbf{tr}}}
\newcommand{\rmk}{{\mathcal{K}}}
\newcommand{\I}{{\mathrm{I}}}
\newcommand{\E}{{\mathrm{E}}}
\newcommand{\B}{{\mathcal{B}}}
\newcommand{\bmo}{{\bm{o}}}
\newcommand{\R}{{\mathbb{R}}}
\newcommand{\cov}{{\mathrm{Cov}}}
\newcommand{\Log}{\text{Log}}
\newcommand{\M}{\mathcal{M}}
\newcommand{\refeq}[1]{{eq.~(\ref{#1})}}

\newcommand{\ProjMean}{{\widehat{\bm S}_E}}
\newcommand{\ProjMedian}{{\widetilde{\bm S}_E}}
\newcommand{\GeomMean}{{\widehat{\bm S}_R}}
\newcommand{\GeomMedian}{{\widetilde{\bm S}_R}}
\newcommand{\Rdist}{{d_R}}
\newcommand{\Edist}{{d_E}}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcommand{\blue}[1]{{\color{blue} #1}}
\newcommand{\red}[1]{{\color{red} #1}}
\newcommand{\green}[1]{{\color{green} #1}}
\newcommand{\hh}[1]{{\color{orange} #1}}

%\pagestyle{plain}
%\bibliographystyle{plainnat}
\bibliographystyle{abbrvnat}
\setcounter{section}{0}
\bibpunct{(}{)}{;}{a}{,}{;}
\graphicspath{{images/}}
%\setlength{\parindent}{0pt}
\begin{document}

\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

\if0\blind
{
  \title{\bf Point Estimation of the Central Orientation of Random Rotations}
  \author{Bryan Stanfill\\
    Ulrike Genschel \\
    and\\
    Heike Hofmann\\
    Department of Statistics, Iowa State University\\}
  \maketitle
} \fi

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Point Estimation of the Central Orientation of Random Rotations}
\end{center}
  \medskip
} \fi

%\title{Point Estimation of the Central Orientation of Random Rotations}
%\author{Bryan Stanfill, Ulrike Genschel, Heike Hofmann}
%\date{\today}


%\begin{comment}
\bigskip
\begin{abstract}
%\footnotesize
Data as three-dimensional rotations have application in computer science, kinematics and materials sciences, among other areas.  Estimating the central orientation from a sample of such data is an important problem, which is complicated by the
fact that several different approaches exist for this,  motivated by various geometrical and decision-theoretic considerations. However, little is known about how such estimators compare, especially on common distributions for location models with random rotations.  We examine four location estimators, three of which are commonly found in different literatures and the
fourth estimator (a projected median) is newly introduced.  Our study unifies
existing literature and provides a detailed numerical investigation of location estimators for three commonly used rotation distributions in statistics and materials science.  While
the data-generating model influences the best choice of an estimator, the proposed projected median emerges as an overall good performer, which can be suggested
without particular distributional assumptions.  We illustrate the estimators 
and our findings with data from a materials science study by approximating the central orientation of cubic crystals on the micro-surface of a metal. Accompanying supplemental materials are available online.


\noindent\textit{Keywords}: Cayley distribution, Electronic Backscatter Diffraction, Geodesic distance, Matrix Fisher distribution, Projected median,  Rotation Group \end{abstract}
%\end{comment}
\spacingset{1.45} % DON'T change the spacing!
%\doublespace
\newpage
\input{introductionV07}
\input{backgroundV07}
\input{estimatorsV08}
\input{simulationV07}
\input{resultsV07}
\input{dataV03}
\input{DiscussionV04}
\clearpage
\bibliography{bing}
%\clearpage
%\input{appendixV03}
\end{document}

